Uncertainty propagation in neural networks for sparse coding

### 2018-03-10 paper/BayesianLISTA.tex
figure corrections

\begin{figure}[t]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}}
%\caption{Approximation of propagation through soft thresholding}
%\label{fig:z_new_testing}
\end{figure}

>>>>

\begin{figure}[t]
\subfloat[Approximation of the \newline product of Gaussians]{\includegraphics[width=0.5\columnwidth]{d_testing}\label{fig:d_testing}}
%\label{fig:d_testing}
\subfloat[Approximation of the propagation through soft thresholding]{\includegraphics[width=0.5\columnwidth]{z_new_testing}\label{fig:z_new_testing}}
\caption{Approximations of Bayesian \textsc{lista}}
%\label{fig:z_new_testing}
\end{figure}
